Coherent optical association of a single molecule

### 2020-11-07 paper.tex
Update on Overleaf.

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$ (\textcolor{red}{Unresolved comment from Jon: with so many digits on the resonance frequency, we may need to mention more digits on the B field number and/or also state the tweezer power. We can state the tweezer power for where we measure it, but the transmission through the objective, etc. I believe is only estimated. (YYC: This is why the original number quoted was zero field. The current number is still for zero tweezer power), May also need to quote tweezer waist for power dependency}\todo{})
  with more than $60~\mathrm{\%}$ of the molecule created in the motional ground state.
  This technique does not rely on narrow excited state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Yao2018, Wall2015, Sundar2018, wall2015realizing}, quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111,Segev2019}.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049, PhysRevLett.121.013202, PhysRevLett.120.123201}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020,He331}  have been achieved through the association of ultracold atoms.
% (any place to cite  molecular ion work?)
% Citations are not complete. Add them as you see fit.

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques that have been developed for atoms. Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy. A two-step approach has been demonstrated to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance. The only exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}. With these requirements, dimers between alkali atoms and non-magnetic atoms, or molecules involving atoms without narrow intercombination lines remain difficult to associate.
% These requirements limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly-bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a. The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state. The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state. A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation. To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible. This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control.

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematics of the optical transition from an atom pair to a weakly-bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (b) Comparison between using a weakly-bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (c) Enhancement of short range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\text{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state, and the target weakly-bound molecular state are coupled to an intermediate state by two laser  with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
The transfer Raman Rabi Rate, $\Omega_R=\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_s$
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}.
Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the target molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally. Thus, the scattering is given by $ \Gamma_s=\Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.

Early experiments used weakly-bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, for a complete picture, the many excited vibrational states in a molecular potential
as well as the excited atomic continuum need to be considered.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly-bound excited state as the intermeidate state
suffers from strong scattering of the nearby excited atomic continuum, resulting in large incoherence and loss to other molecular states.
This scattering is proportional to $1/\delta_{\mathrm{thresh}}^2$,
where $\delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency
and scattering rate at different detunings from the atomic threshold
taking into account of all states of
the $\mathrm{c^3\Sigma^+}(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
and the continuum~\cite{Liu2017}.
The excited atomic continuum is particularly important for the target molecular state.
The sum of the squares of the wavefunction overlap
between the target weakly-bound molecular state
and all the excited molecular bound states is only about $0.02$,
suggesting that there is significant matrix element
between the target molecular state and the excited atomic continuum (See SM \todo{proper cite}).
This calculation shows that the ratio of the Raman Rabi rate to scattering rate
can be made larger for more deeply bound states compared to weakly-bound states
at a cost of a smaller Raman Rabi frequency
(Fig.~\ref{f-theory}b, full result in SM \todo{proper cite})
As a result, we choose the $v'=0$ of $\mathrm{c^3\Sigma^+}(\Omega = 1)$ as an intermediate state
to drive the Raman transition.

@@

maximizes Raman Rabi coupling at a given detuning.

@@

the coupling $\Omega_a$ is approximately proportional to

@@

the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $,
where $ \omega_{\text{trap}} $ is the trap frequency\cite{Mies2000}.

@@

For the target molecular state, we perform coupled-channel calculations
to identify the Rabi frequencies $\Omega_m$ to different weakly-bound spin states. The target's spin state is ideally similar to the initial spin state in order to minimize sensitivity to the B-field.

@@

Coupled channel calculations show that this target molecular state also has reduced Rabi frequency, $ \Omega_m $,
with the intermediate state when compared to bound states of the other stable spin combinations, thus further increasing the $\Omega_a/\Omega_m$ ratio.

@@

Using an initial $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination

@@

with the other combinations, and thus relaxing the intensity stability requirement to the few percent level. % Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.

@@

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (a) Raman detuning scans at different times showing the resonance frequency.
    (b) Raman pulse time scan on resonance.
    A decaying Rabi oscillation can be observed proving the coherence of
    the Raman transfer process.
    This is fitted together with (a) to a model of Raman transition
    with loss on the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$
    which defines the location of the atoms and molecule.
    We use a bias B field of $B_0=8.8~\mathrm{G}$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    \label{f-raman}}
\end{figure}

%% Preparation
Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}. In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\Na$ atom and a single ${}^{133}\Cs$ atom into separate optical tweezers. The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom to be able to post select the experimental result on the initial loading condition. Raman sideband cooling is then applied to cool both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers. After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs} $ %and are merged into the same tweezer~\cite{Liu2019}. %The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $.
which has a small scattering length. The small two atom interaction allows the merging of the two atoms to be done with minimum pertubation so that they remain in the motional ground state.

% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.  %using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\Cs}}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
This spin flip selectively transfers atoms in the relative motion ground state, removing any initial hot atom background from imperfect cooling \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}. For the experiment reported here, $31~\mathrm{\%}$ of our initial two atom population is successfully transferred.
% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform Raman transfer of an atom pair to the target weakly-bound molecular state, we use the tweezer beam itself as the Raman beams by turning on two frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset). The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time. Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states. % to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
% In addition to reducing the number of laser beams during the Raman transition,

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{fig3.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime in $3.75~\mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in $3.75~\mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$ on a log-log scale,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}

>>>>

\begin{abstract}
  Fully controlled single molecules provide a promising platform for a variety of quantum science applications. As a step towards this goal, we report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$ 
  with more than $60~\mathrm{\%}$ of the molecule created in the motional ground state.
  This technique does not rely on narrow excited state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Micheli2006, Yao2018, Wall2015, wall2015realizing}, quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019}, and studies of ultracold chemistry~\cite{Bala2016,Hu1111,Segev2019,deJongh626}.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049, PhysRevLett.121.013202, Truppe2017}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020,He331}  have been achieved through the association of ultracold atoms.
% (any place to cite  molecular ion work?)
% Citations are not complete. Add them as you see fit.

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques that have been developed for atoms. Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy. A two step approach has been demonstrated to associate atom pairs into weakly bound molecules first, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance. The only exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}. With these requirements, molecules involving non-magnetic atoms or atoms without narrow intercombination lines remain difficult to associate.
% These requirements limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a. The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state. The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state. A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation. To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible. This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control.

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematic of the optical transition from an atom pair to a weakly-bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (b) Comparison between using a weakly-bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (c) Enhancement of the short range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\text{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
The transfer Raman Rabi Rate, $\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}.
Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the target molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally. Thus, the scattering rate is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.

Early experiments used weakly bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, for a complete picture, the many excited vibrational states in a molecular potential
as well as the excited atomic continuum need to be considered.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly bound excited state as the intermediate state
suffers from strong scattering of the nearby excited atomic continuum, resulting in large incoherence and loss to other molecular states.
This scattering is proportional to $1/\delta_{\mathrm{thresh}}^2$,
where $\delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency $\Omega_R$
and scattering rate $\Gamma_s$ at different detunings from the atomic threshold
taking into account of all states of
the $\mathrm{c^3\Sigma^+}(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
and the continuum~\cite{Liu2017}.
The excited atomic continuum is particularly important for the target molecular state.
The sum of the squares of the wavefunction overlap
between the target weakly-bound molecular state
and all the excited molecular bound states is only about $0.02$,
suggesting that there is significant matrix element
between the target molecular state and the excited atomic continuum (See Supplementary Material\todo{proper cite}).
This calculation shows that the ratio of the Raman Rabi rate to scattering rate
can be made larger for more deeply bound states compared to weakly bound states
at a cost of a smaller Raman Rabi frequency
(Fig.~\ref{f-theory}b, full result in Supplementary Material \todo{proper cite})
As a result, we choose the $v'=0$ of $\mathrm{c^3\Sigma^+}(\Omega = 1)$ as an intermediate state
to drive the Raman transition.

@@

maximizes the Raman Rabi frequency at a given detuning.

@@

$\Omega_a$ is approximately proportional to

@@

the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,
where $ \omega_{\text{trap}} $ is the trap frequency and $P$ is the power in the trap\cite{Mies2000}. However, additional power may not always be available, and will also lead to additional undesired scattering.

@@

For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.

@@

Coupled channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $,
with the intermediate state when compared to bound states of the other spin compositions. This further increases the $\Omega_a/\Omega_m$ ratio when using the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.

@@

This combination

@@

with the other combinations, thus relaxing the intensity stability requirement to the few percent level. % Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.

@@

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (a) Raman detuning scans at different times showing the resonance frequency.
    (b) Raman pulse time scan on resonance.
    A decaying Rabi oscillation can be observed proving the coherence of
    the Raman transfer process.
    This is fitted together with (a) to a model of the Raman transition including loss of the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$
    which defines the location of the atoms and molecule.
    We use a bias B field of $B_0=8.8~\mathrm{G}$ along the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    \label{f-raman}}
\end{figure}

%% Preparation
Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}. In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\Na$ atom and a single ${}^{133}\Cs$ atom into separate optical tweezers. The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom to be able to post select the experimental result on the initial loading condition. Raman sideband cooling is then applied to prepare both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers. After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs} $ %and are merged into the same tweezer~\cite{Liu2019}. %The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $.
which has a small scattering length. The small two atom interaction allows the merging of the two atoms to be done with minimum pertubation so that they remain in the motional ground state.

% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
Next, we drive the atoms into the large scattering length $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.  %using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\Cs}}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
This spin flip selectively transfers atoms in the relative motional ground state, removing any initial hot atom background from imperfect cooling \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motional ground state.}. For the experiment reported here, $31~\mathrm{\%}$ of our initial two atom population is successfully transferred.
% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform the Raman transfer of an atom pair to the target weakly bound molecular state, we use the tweezer beam itself as the Raman beams by turning on two frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset). The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time. Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states. % to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
% In addition to reducing the number of laser beams during the Raman transition,

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{fig3.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime in $3.75~\mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in $3.75~\mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$ on a log-log scale,
    this is consistent with a two-photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}
